The locations of features in the mass distribution of merging binary black holes are robust against uncertainties in the metallicity-dependent cosmic star formation history.

### 2023-01-28 src/tex/ms.tex
minor change text values
minor rephrasing in text

\begin{deluxetable*}{clr | cl}
\label{tab: fit params}
\tablecaption{Best fitting parameters for our \SFRDzZ fit to TNG100 data.}
\tablehead{\colhead{dP/dZ } & \colhead{description} & \colhead{best fit} &  \colhead{SFRD(z)} & \colhead{best fit} \\
 \colhead{ } & \colhead{} & \colhead{}  & \colhead{$\Msun\yr^{-1}\Mpc^{-3}$} & \colhead{} } 
\startdata
$\mu_0$    & mean metallicity at $z=0$    & $0.025  \pm 0.036$ &  $a$ &  $0.02 \pm 0.072$ \\% \, \Msun\yr^{-1}\Mpc^{-3}$\\
$\mu_z$    & $z$-dependence of the mean   & $-0.048 \pm 0.006$ &  $b$ &  $1.48 \pm 0.002$\\
$\alpha$   & shape (skewness)             & $-1.778 \pm 0.002$ &  $c$ &  $4.44 \pm 0.001$\\
$\omega_0$ & scale at $z=0$               & $1.122  \pm 0.001$ &  $d$ &  $5.90 \pm 0.002$\\
$\omega_z$ & $z$-dependence of the scale  & $0.049  \pm 0.009$ &   \\
\enddata
\end{deluxetable*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{deluxetable}{cccc}
\label{tab: fit variations}
\tablewidth{0.5\textwidth} 
\tablecaption{\edit1{Variations on \SFRDzZ. 
For every variation, we either swap the value of an individual \dpdZ parameter, or exchange the set of four \SFRDz parameters, and replace them by the the min/max values listed here. All other parameters are kept fixed at their fiducial value. }}
\tablehead{\colhead{} & \colhead{min} & \colhead{fiducial} & \colhead{max} } 
\startdata
\dpdZ &       &  &  \\
$\mu_0$          &   0.007   & $0.025$  &  0.035  \\
$\mu_z$          &   0.0   & $-0.048$ &   -0.5 \\
$\alpha$         &   -6.0   & $-1.778$ &  0.0  \\
$\omega_0$       &   0.7   & $1.125$  &  2.0  \\
$\omega_z$       &   0.0   & $0.048$  &  0.1  \\ \hline
\SFRDz &       &  &  \\
($a$,$b$ ... &  ($0.01$, $2.60$   & ($0.02$, $1.48$ &  ($0.03$, $2.6$ \\
... $c$,$d$) &  $3.20$, $6.20$)   & $4.44$, $5.90$) &   $3.3$, $5.9$) \\
\enddata
\end{deluxetable}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

For the cosmic metallicity density distribution, we vary every parameter that determines the shape of \dpdZ independently (left two columns of Table \ref{tab: fit params}), while keeping all other parameters fixed at their fiducial value.
For each variation, we inspect the fraction of stellar mass that is formed at low-metallicity ($Z<0.1 Z_{\odot}$) versus the fraction of stellar mass that is formed at high-metallicity ($Z> Z_{\odot}$), for all star formation that occurred below a certain threshold redshift.
We compare this to the models from \cite{Chruslinska+2021} in Figure \ref{fig: low high Z fraction} in Appendix \ref{app: reasonable var}.
We have chosen our variations such that they span a reasonable range of cosmic metallicity density distributions as allowed by observation-based and cosmological simulations-based models.
We use the models \texttt{214-f14SB-BiC\_FMR270\_FOH\_z\_dM.dat}, and \texttt{302-f14SB-Boco\_FMR270\_FOH\_z\_dM.dat} from \cite{Chruslinska+2021}\footnote{These models \edit1{ including a detailed description of their contents } are publicly available at \url{https://ftp.science.ru.nl/astro/mchruslinska/Chruslinska_et_al_2021/} } as a representation of a very low and high metallicity star formation realisation respectively. These models are the low and high metallicity extreme under their fiducial SFR–metallicity correlation, 
%
\edit1{and so we will refer to them as \texttt{Chr21\_lowZ} and \texttt{Chr21\_highZ} respectively from hereon. The difference between these models lies in the assumptions in the underlying empirical galaxy relations. In general, low-mass galaxies contribute to low-metallicity star formation and shift the peak of \SFRDzZ to lower metallicities. }
% lowZ model: 2: sharp flattening (high mass part of the SFMR), 1: alpha\_fix(z) (low mass end of the GSMF), 4: PP04 (MZR at $z\approx0$) -- 
% Starburst galaxies are treated as in BiC : the properties of starbursts are based on the studies of Bisigello+18 and Caputi+17 -- 
% nabla\_FMR0 = 0.27 dex, describing the strength of the SFR-metallicity correlation in the high SFR, low mass regime. }
%
\edit1{\texttt{Chr21\_lowZ} is characterised by a star formation–galaxy mass relation that is flat at high galaxy masses (reducing the star formation rate for the highest-mass galaxies), a galaxy stellar mass function that evolves with redshift (predicting an increasing number density of low-mass galaxies), 
and a galaxy mass-metallicity relation following \cite{PettiniPagel2004}. 
This model further approximates the contribution of starburst galaxies following \cite{Bisigello+2018} and \cite{Caputi+2017}. Including starbursts shift the peak of \SFRDzZ to lower metallicities and broadens the low metallicity part of the distribution.
}
% highZ model: 3: no flattening (high mass part of the SFMR), 0: alpha\_fix = -1.45 (low mass end of the GSMF), 2: KK04a (MZR at $z\approx0$) --  
% Starburst galaxies are treated as in  Boco : the properties of starbursts are based on the studies of Sargent+12/Bethermin+12, as used in Boco+21. -- 
% nabla\_FMR0 = 0.27 dex, describing the strength of the SFR-metallicity correlation in the high SFR, low mass regime.}
%
\edit1{On the other hand, \texttt{Chr21\_highZ} assumes the star formation–galaxy mass relation does not flatten towards higher galaxy masses, a galaxy stellar mass function that is constant over redshift, and a galaxy mass-metallicity relation following \cite{KobulnickyKewley2004}. Lastly, this model adopts the starburst prescription from \cite{Boco+2021}, which produces results that are similar to models without starburst galaxies. 
}

@@

Lastly, we consider two variations of the overall star-formation rate density, \SFRDz, where we keep the metallicity distribution \dpdZ fixed, but vary all four \SFRDz parameters at once (right two columns of Table \ref{tab: fit params}). 
We use Figure 11 from \cite{Chruslinska+2021} to determine approximate upper and lower bounds to the overall star-formation rate density. We choose \cite{Madau+2017} as an approximation of the lower limit. 
For the upper limit, we use the upper edge of 
\edit1{ models that adopt starbursts following \cite{Bisigello+2018} and \cite{Caputi+2017} (\texttt{SB: B18/C17}), combined}
with a non-evolving low-mass end of the galaxy stellar mass function \citep[shown as a thick brown line in Fig. 11 of ][and described in their table B1]{Chruslinska+2021}.
% for the \texttt{SB: B18/C17} model variations (i.e. ) with a non-evolving low-mass end of the galaxy stellar mass function \citep[table B1 from][also shown as thick brown line in their Fig. 11]{Chruslinska+2021}. 
To approximate these models, we fit equation \ref{eq: sfr1} by eye to the broken power law description of this model as presented in appendix B1 of \cite{Chruslinska+2021}.
We show all \SFRDz variations in Figure~\ref{fig: SFR(z)}. \\

>>>>

\begin{deluxetable*}{clr | cl}
\label{tab: fit params}
\tablecaption{Best fitting parameters for our \SFRDzZ fit to TNG100 data.}
\tablehead{\colhead{dP/dZ } & \colhead{description} & \colhead{best fit} &  \colhead{SFRD(z)} & \colhead{best fit} \\
 \colhead{ } & \colhead{} & \colhead{}  & \colhead{$\Msun\yr^{-1}\Mpc^{-3}$} & \colhead{} } 
\startdata
$\mu_0$    & mean metallicity at $z=0$    & $0.025  \pm 0.036$ &  $a$ &  $0.02 \pm 0.072$ \\% \, \Msun\yr^{-1}\Mpc^{-3}$\\
$\mu_z$    & $z$-dependence of the mean   & $-0.049 \pm 0.006$ &  $b$ &  $1.48 \pm 0.002$\\
$\alpha$   & shape (skewness)             & $-1.778 \pm 0.002$ &  $c$ &  $4.44 \pm 0.001$\\
$\omega_0$ & scale at $z=0$               & $1.122  \pm 0.001$ &  $d$ &  $5.90 \pm 0.002$\\
$\omega_z$ & $z$-dependence of the scale  & $0.049  \pm 0.009$ &   \\
\enddata
\end{deluxetable*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{deluxetable}{cccc}
\label{tab: fit variations}
\tablewidth{0.5\textwidth} 
\tablecaption{\edit1{Variations on \SFRDzZ. 
For every variation, we either swap the value of an individual \dpdZ parameter, or exchange the set of four \SFRDz parameters, and replace them by the the min/max values listed here. All other parameters are kept fixed at their fiducial value. }}
\tablehead{\colhead{} & \colhead{min} & \colhead{fiducial} & \colhead{max} } 
\startdata
\dpdZ &       &  &  \\
$\mu_0$          &   0.007   & $0.025$  &  0.035  \\
$\mu_z$          &   0.0   & $-0.049$ &   -0.5 \\
$\alpha$         &   -6.0   & $-1.778$ &  0.0  \\
$\omega_0$       &   0.7   & $1.125$  &  2.0  \\
$\omega_z$       &   0.0   & $0.048$  &  0.1  \\ \hline
\SFRDz &       &  &  \\
($a$,$b$ ... &  ($0.01$, $2.60$   & ($0.02$, $1.48$ &  ($0.03$, $2.6$ \\
... $c$,$d$) &  $3.20$, $6.20$)   & $4.44$, $5.90$) &   $3.3$, $5.9$) \\
\enddata
\end{deluxetable}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

For the cosmic metallicity density distribution, we vary every parameter that determines the shape of \dpdZ independently (\edit1{three left-most columns of Table \ref{tab: fit params}, and top of Table \ref{tab: fit variations} }), while keeping all other parameters fixed at their fiducial value.
For each variation, we inspect the fraction of stellar mass that is formed at low-metallicity ($Z<0.1 Z_{\odot}$) versus the fraction of stellar mass that is formed at high-metallicity ($Z> Z_{\odot}$), for all star formation that occurred below a certain threshold redshift.
We compare this to the models from \cite{Chruslinska+2021} in Figure \ref{fig: low high Z fraction} in Appendix \ref{app: reasonable var}.
We have chosen our variations such that they span a reasonable range of cosmic metallicity density distributions as allowed by observation-based and cosmological simulations-based models.
We use the models \texttt{214-f14SB-BiC\_FMR270\_FOH\_z\_dM.dat}, and \texttt{302-f14SB-Boco\_FMR270\_FOH\_z\_dM.dat} from \cite{Chruslinska+2021}\footnote{These models \edit1{ including a detailed description of their contents } are publicly available at \url{https://ftp.science.ru.nl/astro/mchruslinska/Chruslinska_et_al_2021/} } as a representation of a very low and high metallicity star formation realisation respectively. These models are the low and high metallicity extreme under their fiducial SFR–metallicity correlation, 
%
\edit1{and so we will refer to them as \texttt{Chr21\_lowZ} and \texttt{Chr21\_highZ} respectively from hereon. The difference between these models lies in the assumptions in the underlying empirical galaxy relations. In general, low-mass galaxies contribute to low-metallicity star formation and shift the peak of \SFRDzZ to lower metallicities. }
% lowZ model: 2: sharp flattening (high mass part of the SFMR), 1: alpha\_fix(z) (low mass end of the GSMF), 4: PP04 (MZR at $z\approx0$) -- 
% Starburst galaxies are treated as in BiC : the properties of starbursts are based on the studies of Bisigello+18 and Caputi+17 -- 
% nabla\_FMR0 = 0.27 dex, describing the strength of the SFR-metallicity correlation in the high SFR, low mass regime. }
%
\edit1{\texttt{Chr21\_lowZ} is characterised by a star formation–galaxy mass relation that is flat at high galaxy masses (reducing the star formation rate for the highest-mass galaxies), a galaxy stellar mass function that evolves with redshift (predicting an increasing number density of low-mass galaxies), 
and a galaxy mass-metallicity relation following \cite{PettiniPagel2004}. 
This model further approximates the contribution of starburst galaxies following \cite{Bisigello+2018} and \cite{Caputi+2017}. Including starbursts shift the peak of \SFRDzZ to lower metallicities and broadens the low metallicity part of the distribution.
}
% highZ model: 3: no flattening (high mass part of the SFMR), 0: alpha\_fix = -1.45 (low mass end of the GSMF), 2: KK04a (MZR at $z\approx0$) --  
% Starburst galaxies are treated as in  Boco : the properties of starbursts are based on the studies of Sargent+12/Bethermin+12, as used in Boco+21. -- 
% nabla\_FMR0 = 0.27 dex, describing the strength of the SFR-metallicity correlation in the high SFR, low mass regime.}
%
\edit1{On the other hand, \texttt{Chr21\_highZ} assumes the star formation–galaxy mass relation does not flatten towards higher galaxy masses, a galaxy stellar mass function that is constant over redshift, and a galaxy mass-metallicity relation following \cite{KobulnickyKewley2004}. Lastly, this model adopts the starburst prescription from \cite{Boco+2021}, which produces results that are similar to models without starburst galaxies. 
}

@@

We also consider two variations of the overall star-formation rate density, \SFRDz, where we keep the metallicity distribution \dpdZ fixed, but vary all four \SFRDz parameters at once (right two columns of Table \ref{tab: fit params} \edit1{, and bottom of Table \ref{tab: fit variations} }). 
We use Figure 11 from \cite{Chruslinska+2021} to determine approximate upper and lower bounds to the overall star-formation rate density. We choose \cite{Madau+2017} as an approximation of the lower limit. 
For the upper limit, we use the upper edge of 
\edit1{ models that adopt starbursts following \cite{Bisigello+2018} and \cite{Caputi+2017} (\texttt{SB: B18/C17}), combined}
with a non-evolving low-mass end of the galaxy stellar mass function \citep[shown as a thick brown line in Fig. 11 of ][and described in their table B1]{Chruslinska+2021}.
% for the \texttt{SB: B18/C17} model variations (i.e. ) with a non-evolving low-mass end of the galaxy stellar mass function \citep[table B1 from][also shown as thick brown line in their Fig. 11]{Chruslinska+2021}. 
To approximate these models, we fit equation \ref{eq: sfr1} by eye to the broken power law description of this model as presented in appendix B1 of \cite{Chruslinska+2021}.
We show all \SFRDz variations in Figure~\ref{fig: SFR(z)}. \\
